\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
%\usepackage{hyperref}
\usepackage[hidelinks]{hyperref}


%\pagestyle{fancy}
%\fancyhf{}
%\lhead{Partha Pratim Ray}
%\rhead{Page \thepage}
%\lfoot{parthapratimray1986@gmail.com}
%\rfoot{https://github.com/ParthaPRay}

\input{glyphtounicode}

\pdfgentounicode=1

\begin{document}
	
	% Header Section
	\begin{center}
		\textbf{\Large Partha Pratim Ray}\\
		\vspace{2mm}
		C/O, Ranajit Kumar Ray, Netaji Road, By Lane 2, Newtown, Cooch Behar, WB 736101, India \\
    Mobile: +917908402850 | Email: \href{mailto:parthapratimray1986@gmail.com}{parthapratimray1986@gmail.com}\\
		LinkedIn: \href{https://www.linkedin.com/in/partha-pratim-ray-9a6491216}{https://www.linkedin.com/in/partha-pratim-ray-9a6491216} \\
		GitHub: \href{https://github.com/ParthaPRay}{https://github.com/ParthaPRay} \\
		Google Scholar: \href{https://scholar.google.com/citations?user=ioplfagAAAAJ}{https://scholar.google.com/citations?user=ioplfagAAAAJ}\\
		\vspace{2mm}
	%	\hrule
	%	\vspace{1mm}
	\end{center}
	
	\vspace*{-8mm}	
	
	% Objective or Summary
	\section*{Summary}
	\vspace*{-2.5mm}
	\hrule 
	\vspace*{2mm}
	11+ years of experience in Edge Computing, IoT, Edge-AI Analytics, Edge-Cloud Integration, AI in Innovation, Pervasive AI, Generative AI in multiple organizations including academia and applied Industry 4.0. Having strong hands-on technical and leadership knowledge in IoT ecosystem development and management. Published more than 105 journal and 29 conference articles and 3 book chapters, filed 7 national patents and wrote 7 books. Volunteered in IEEE CTSoC, IEEE DewCom STC. Collaborative work experience with reputed international organizations. 
	
	\vspace*{-3mm}	
		
		
			% Skills
		\section*{Skills}
		\vspace*{-2.5mm}
		\hrule 
		\vspace*{2mm}

	
		\textbf{Edge Analytics:} PubNub, EON Visualizer API, Node.js, Johnny-Five, Chart.js, Socket.io, Express Server, Flot.js, jQuerym, Apache Edgent
		\\
		\textbf{Python:} Pandas, NumPy, scikit-learn, Seaborn, Matplotlib, PCA, Regression, Classification, Clustering
		\\
		\textbf{R:} Anomaly Detection, Time Series Forecasting
		\\	
		\textbf{Generative AI:} ChatGPT, Custom ChatGPT Design, ChatGPT Data Analytics, ChatGPT API Integration, Google Bard, LangChain
		\\    	
		\textbf{Communication:} MQTT, GPIO, Bluetooth, WiFi, nRF24L01 2.4GHz, GSM, RF 433MHz, Serial, LoRa, I2C, UART, SPI, Visible Light Communication 
		\\
	\textbf{IoT Programming:} Arduio IDE, Thonny Python IDE, Lua, FreeRTOS, C
	\\	
\textbf{IoT Cloud:} ThingSpeak, ThingsBoard, ThingWorx, IBM Watson IoT, Arduino Cloud, Carritos, Nimbits, Plotly, Temboo, Xively, Ayla's Cloud Fabric, Sensor Cloud, TheThingsIO, SeeControl
		\\
\textbf{Microcontroller:} Arduino Uno, Arduino Nano, Arduino Mega, Arduino Nano 33 BLE Sense, Wemos D1 Mini, ESP8266, ESP32, NodeMCU, BLEDuino, Arduino YUN, Lilypad, Arduino Duemilanove, Arduino MKR1000, Raspberry Pi, Raspberry Pi Pico, PHPoC, Digistamp ATtiny 85, 8051, Intel Galileo \\
		\textbf{Research \& Publication:} Literature Review, Literature Survey, Systematic Analysis, Meta Analysis, SWOT Analysis, Research Article, Latex 

    
		\vspace*{-3mm}
		
	
	% Experience
\section*{Experience}
\vspace*{-2.5mm}
\hrule 
\vspace*{2mm}
  \noindent\textbf{Sikkim University (Central University)} \hfill \textit{July, 2012 - Till Date}\\
  \textit{\underline{Assistant Professor}} \\
  \vspace*{-4mm}
    \begin{itemize}[leftmargin=*]
	\item Facilitated student learning as a researcher, providing guidance and mentorship.
	    \vspace*{-2.5mm}
	\item Led the consultancy for the establishment of Intel IoT Center. 
	\vspace*{-2.5mm}
	\item Ensured successful implementation and strategic development.
	    \vspace*{-2.5mm}
	\item Provided key inputs in policy making and entrepreneurship cell monitoring.  
	\end{itemize}

  \noindent\textbf{Surendra Institute of Engineering and Management} \hfill \textit{January, 2012 - June, 2012}\\
  \textit{\underline{Assistant Professor}} \\
\vspace*{-4mm}
\begin{itemize}[leftmargin=*]
	\item Dispensed as a researcher and guided students towards learning.

\end{itemize}


	\vspace*{-5mm}	

    
    	% Education
    \section*{Education}
    \vspace*{-2.5mm}
    \hrule 
    \vspace*{2mm}
 
\noindent     \textbf{Sikkim University, PhD}\\
 \textit{Pursuing}\\
 Major: IoT and AI\\
    
 \vspace*{-2mm}
 
 \noindent    \textbf{West Bengal University of Technology, M.Tech.}\\
    \textit{November, 2011}\\
    Major: Embedded Systems (9.60 DGPA)\\
    
   
    \vspace*{-2mm}
    
    \noindent
    \textbf{West Bengal University of Technology, B.Tech.}\\
    \textit{August, 2008}\\
    Major: Computer Science and Engineering (8.15 DGPA)\\
    
    
    \vspace*{-7mm}	
       		
    % Certifications 
    \section*{Projects}
    \vspace*{-2.5mm}
    \hrule 
    \vspace*{2mm}
    \begin{itemize}[leftmargin=*]
                	\vspace*{1mm}
  \item Pioneered the design of a Leaf Monitoring System for plant health temperature assessment using IoT.
\vspace*{-6mm}
\item Engineered a web-based information system for medicinal and aromatic plants using React and GitHub hosting.
\vspace*{-2mm}
\item Orchestrated the development of a web-based application for a pipeline inspection robot utilizing IoT technology.
\vspace*{-2mm}
\item Spearheaded the creation of a smart irrigation system leveraging IoT capabilities.
\vspace*{-2mm}
\item Founded the Intel IoT Center, establishing a cornerstone for IoT innovation.
\vspace*{-2mm}
\item Directed comprehensive studies on time series databases tailored for IoT applications.
\vspace*{-2mm}
\item Innovated a second-generation smart irrigation system with enhanced IoT integration.
\vspace*{-2mm}
\item Championed the development of a web-based application for dynamic graphical data visualization using TypeScript.
\vspace*{-2mm}
\item Conceptualized Boilerplate-as-a-Service for real-time health monitoring through IoT.
\vspace*{-2mm}
\item Devised a strategy for electronic health record transmission over a blockchain-assisted decentralized network using IPFS.
\vspace*{-2mm}
\item Analyzed and refined rating algorithms for e-commerce business sites, boosting operational efficiency.
\vspace*{-6mm}
\item Led the deployment of Apache Edgent, enhancing IoT design functionalities.
\vspace*{-2mm}
\item Developed an interoperable and heterogeneous IoT smart gateway, facilitating seamless device communication.
\vspace*{-2mm}
\item Masterminded the design of an IoT-based autonomic robot, integrating cutting-edge technology.
\vspace*{-2mm}
\item Deployed visible light communication between two IoT devices using 650nm laser.
\vspace*{-2mm}
\item Created an engaging Android quiz application, enhancing user interaction and learning.    \end{itemize}
     		
	% Certifications 
	\section*{Certifications}
	\vspace*{-2.5mm}
	\hrule 
	\vspace*{2mm}
	\begin{itemize}[leftmargin=*]
		\item Completed Mastering Digital Twins, accredited by Coursera June, 2019.
		\vspace*{-2mm}
		\item	Certified Blockchain Expert-V2, accredited by the Blockchain Council, during October, 2018.
			\vspace*{-2mm}
			\item	Completed Blockchain and Bitcoin Fundamentals, accredited by Udemy during October, 2018.
			\vspace*{-2mm}
		\item	Completed Blockchain Advanced Level: Uses Beyond Bitcoin 2018, accredited by Udemy during October, 2018.
		
	\end{itemize}
	
	
	% Awards
	\section*{Awards}
	\vspace*{-2.5mm}
	\hrule 
	\vspace*{2mm}
	\begin{itemize}[leftmargin=*]
		\item Earned recognized as Top 2\% Scientists by the Stanford University during 2020 - 2023.
		\vspace*{-2mm}
		\item Secured the "IEI Young Engineers Award 2019-20" in 2020.
		\vspace*{-2mm}		
		\item Awarded the "Emerald Literati Awards" in 2019.
				\vspace*{-2mm}	
		\item Achieved the "Young Scientist" award in 2017.
				\vspace*{-2mm}	
		\item Bestowed with the "Bharat Vikas Award" award in 2017.
		\vspace*{-2mm}	
		\item Achieved "Academic Excellence Awards" award in 2017.
				\vspace*{-2mm}	
		\item Attained the "Young Achiever Award" award in 2018.
		
		\vspace*{-2mm}	
		\item Selected for the Science Academies’ Summer Research Fellowship Programme in 2013.	
		\vspace*{-2mm}	
		\item  Awarded a Post Graduate Scholarship during 2009 - 2011.	
		
	\end{itemize}
	
	% Volunteer Experience or Projects (if applicable)


\end{document}
